%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{verbatim}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Manny}{Jois}{
%\urlstyle{same}\url{http://debarghyadas.com} \\
\href{mailto:m.k.jois@berkeley.edu}{m.k.jois@berkeley.edu} | 650 504 4702 \\
Berkeley, CA | github.com/mkjois
}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\sectionsep
\subsection{University of California, Berkeley}
\descript{B.S. Electrical Engineering and Computer Science}
Class of 2016
\subsection{GPA: 3.96}
Dean's Honors
\sectionsep


\begin{comment}
\descript{BS in Computer Science}
\location{Expected May 2014 | Ithaca, NY}
Conc. in Software Engineering \\
College of Engineering \\
Dean's List (All Semesters) \\
\location{ Cum. GPA: 3.92 / 4.0 \\
Major GPA: 3.94 / 4.0}
\sectionsep
\end{comment}

\begin{comment}
\subsection{La Martiniere for Boys}
\location{Grad. May 2011|  Kolkata, India}
\sectionsep
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}
\section{Links} 
Github:// \href{https://github.com/deedydas}{\custombold{deedydas}} \\
LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\custombold{debarghyadas}} \\
YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\custombold{DeedyDash007}} \\
Twitter://  \href{https://twitter.com/debarghya_das}{\custombold{@debarghya\_das}} \\
Quora://  \href{https://www.quora.com/Debarghya-Das}{\custombold{Debarghya-Das}}
\sectionsep
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\sectionsep
\begin{comment}
\subsection{Graduate}
Advanced Machine Learning \\
Open Source Software Engineering \\
Advanced Interactive Graphics \\
Compilers + Practicum \\
Cloud Computing \\
\sectionsep
\end{comment}

%\subsection{Undergraduate}
\begin{tightemize}
\item Data Structures \\
\item Machine Structures \\
\item Discrete Mathematics \\
\item Signals and Systems \\
\item Circuits \\
\item Communication Networks \\
\item Algorithms \\
\item Operating Systems \\
\item Programming Language Design and Implementation \\
\item Artificial Intelligence \\
\item Machine Learning (current) \\
\item Randomized Algorithms (current) \\
\item Computational Models of Cognition (current)
\end{tightemize}

\begin{comment}
Information Retrieval \\
Operating Systems \\
Artificial Intelligence + Practicum \\
Functional Programming \\
Computer Graphics + Practicum \\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
Unix Tools and Scripting \\
\end{comment}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\sectionsep
\subsection{Extensive experience}
Python \textbullet{} Java \textbullet{} C \textbullet{}  HTML \textbullet{} CSS \textbullet{} JavaScript \textbullet{} Node.js \textbullet{} jQuery \textbullet{} Angular.js \textbullet{} Git \textbullet{} Bash \textbullet{} Linux \textbullet{} \LaTeX 
\sectionsep
\subsection{Moderate work}
C++ \textbullet{} C\# \textbullet{} Scheme/Church \textbullet{} Data visualization \textbullet{} Classification \textbullet{} Eclipse
\sectionsep
\subsection{Basic exposure}
Hadoop \textbullet{} MATLAB

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.64\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\sectionsep
\runsubsection{Cisco Systems}\\
\descript{| Software Engineering Intern}
\location{May 2014 – Aug 2014 | San Jose, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Devised network topologies used to test performance of the latest iterations of network security appliances
\item Wrote Python scripts to analyze and display results of code coverage test outputs.
\item Team project to develop an internal tool to automatically set up test beds and run tests using driver-building software.
\end{tightemize}
\sectionsep

\runsubsection{Associated Students of the University of California}\\
\descript{| Web Development Team}
\location{Sep 2013 – May 2014 | Berkeley, CA}
\begin{tightemize}
\item Maintained web pages with data critical to the operation of the university student government.
\item Part of the team tasked to transition the organization website (asuc.org) to a new host and framework.
\end{tightemize}
\sectionsep

\runsubsection{Pioneers in Engineering}\\
\descript{| Kit Development Staff}
\location{Sep 2012 – Apr 2013 | Berkeley, CA}
\begin{tightemize}
\item Wrote and documented code for various robot sensors and radios.
\item Worked with graduate students on implementation and integration of a field control system for annual high-school robot competition.
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\sectionsep
\runsubsection{JavaScript Contracts}\\
\location{Nov 2014}
Developed a language embedded in JavaScript to enforce function invariants at all times, as well as conduct simple tests of functions upon loading a script (see github).

\sectionsep
\runsubsection{Language popularity}\\
\location{Sep 2014}
Used d3 to create a visualization of programming language popularity based on a dataset containing years of creation, language paradigm and number of GitHub repositories (see github).

\sectionsep
\runsubsection{UC Berkeley Food Pantry}\\
\location{Jan 2014 – Apr 2014}
Helped create an official website (pantry.asuc.org) for the UC Berkeley Food Pantry, an initiative that looks to provide students who struggle financially with nourishing meals to support them.

\sectionsep
\runsubsection{Hadoop Map-Reduce}\\
\location{Sep 2013}
Machine structures class project using Hadoop's MapReduce framework to analyze large bodies of text using word co-occurrence algorithms. Our program used distributed computing power to determine, given a word, what other words were most associated with it.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}
\section{Awards} 
\sectionsep
\begin{tabular}{rll}
2014	     & top 52/2500  & KPCB Engineering Fellow\\
2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
2013	     & National  & Jump Trading Challenge Finalist\\
2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
\end{tabular}
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\section{Societies} 

\begin{tabular}{rll}
2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
2014   & National   & The Global Leadership and Education Forum (tGELF)\\
2012   &  National  & Golden Key International Honor Society\\
2012   &  National   & National Society of Collegiate Scholars\\
\end{tabular}
\sectionsep
\end{comment}

\end{minipage} 
\end{document}  \documentclass[]{article}
